Notes on Wide Gap

### 2016-05-11 paper/wide_gap_notes.tex
fixed r perturbation to be dr(V) = 1j*kr*V
widegap matrices corrected in notes
coarser Rm search

\beq
\mathcal{L}_0 = \left[\begin{matrix}
\frac{1}{\reye} \left(-\frac{3}{r^4} \partial_r + \frac{3}{r^3} \partial_r^2 - \frac{2}{r^2} \partial_r^3 + \frac{1}{r} \partial_r^4\right) & 0 & 0 & 0\\
0 & \frac{1}{\reye} \left(\partial_r^2 + \frac{1}{r} \partial_r - \frac{1}{r} \right) & 0 & 0 \\
0 & 0 & \frac{1}{\reym} \left(\partial_r^2 - \frac{1}{r} \partial_r\right) & 0 \\
0 & 0 & 0 & \frac{1}{\reym} \left(\partial_r^2 + \frac{1}{r}\partial_r - \frac{1}{r^2}\right)
\end{matrix}\right]
\eeq

\beq
\mathcal{L}_1 = \left[\begin{matrix}
0 & 3\Omega(r) & \frac{2}{\beta} \frac{1}{r} \left(\partial_r^2 - \frac{1}{r}\partial_r\right) & 0 \\
-\frac{4}{r} \Omega(r) - \partial_r \Omega(r) & 0 & 0 & \frac{2}{\beta} \\
1 & 0 & 0 & 0 \\
0 & 1 & \frac{2}{r} \Omega(r)  + \partial_r \Omega(r) & 0
\end{matrix}\right]
\eeq

@@

The MRI is a complicated three-dimensional instability

>>>>

\beq
\mathcal{L}_0 = \left[\begin{matrix}
\frac{1}{\reye} \left(-\frac{3}{r^4} \partial_r + \frac{3}{r^3} \partial_r^2 - \frac{2}{r^2} \partial_r^3 + \frac{1}{r} \partial_r^4\right) & 0 & 0 & 0\\
0 & \frac{1}{\reye} \left(\partial_r^2 + \frac{1}{r} \partial_r - \frac{1}{r^2} \right) & 0 & 0 \\
0 & 0 & \frac{1}{\reym} \left(\partial_r^2 - \frac{1}{r} \partial_r\right) & 0 \\
0 & 0 & 0 & \frac{1}{\reym} \left(\partial_r^2 + \frac{1}{r}\partial_r - \frac{1}{r^2}\right)
\end{matrix}\right]
\eeq

%\beq
%\mathcal{L}_1 = \left[\begin{matrix}
%0 & 3\Omega(r) & \frac{2}{\beta} \frac{1}{r} \left(\partial_r^2 - \frac{1}{r}\partial_r\right) & 0 \\
%-\frac{4}{r} \Omega(r) - \partial_r \Omega(r) & 0 & 0 & \frac{2}{\beta} \\
%1 & 0 & 0 & 0 \\
%0 & 1 & \frac{2}{r} \Omega(r)  + \partial_r \Omega(r) & 0
%\end{matrix}\right]
%\eeq

% work in inertial frame instead
\beq
\mathcal{L}_1 = \left[\begin{matrix}
0 & \frac{2}{r} u_0 & \frac{2}{\beta} \frac{1}{r} \left(\partial_r^2 - \frac{1}{r}\partial_r\right) & 0 \\
(-\frac{1}{r^2} u_0 - \frac{1}{r} \partial_r u_0) & 0 & 0 & \frac{2}{\beta} \\
1 & 0 & 0 & 0 \\
0 & 1 & (\frac{1}{r}\partial_r u_0 - \frac{1}{r^2} u_0) & 0
\end{matrix}\right]
\eeq

@@

-- We locate threshold in the $\reym$ - $k_z$ plane. In the wide-gap case, the growth rate depends much more sensitively on $k_z$ than on $\reym$, while in the thin-gap case the opposite is true. We attribute this to the decreased influence of the boundary layers in the wide-gap geometry. (maybe?)

The complex nature of the MRI means its properties are best parsed in idealized regimes or in simplified geometries. Many studies take
